Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-08-24 paper/main.tex
set surface smoothing from 3 to 2mm
change text from 3 to 2mm

\todo[inline]{only Captions mention smoothing of union of PPAs; Volume FWHM was
2mm, Surface FWHM was 3mm}

@@

% figure group results primary AD & AV contrasts
\begin{figure*}[tbp] \centering
    \includegraphics[width=\linewidth]{figures/group-slices}

@@

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}

    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
      cluster-corrected) of activity correlated with the processing of spatial
      information.
      a) Results are displayed on top of the MNI152 T1-weighted head template,
      with the acquisition field-of-view for the audio-description study
      highlighted.
      The results of the audio-description's primary $t$-contrast (blue) that
      compares geometry-related nouns spoken by the narrator to non-spatial
      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
      on the movie's primary $t$-contrast (red) that compares cuts to a
      setting depicted for the first time with cuts within a recurring setting
      (\texttt{vse\_new > vpe\_old}).
      % PPA
      For comparison depicted as a black outline, the union of the
      individual PPA localization reported by \citet{sengupta2016extension}
      that was spatially smoothed applying a Gaussian kernel with full
      width at half maximum (FWHM) of \unit[2.0]{mm}
      % surface map
      b) The results are displayed as projections onto the reconstructed
      surface of the MNI152 T1-weighted brain template. After projection the
      union of individual PPA localizations was spatially smoothed by a
      Gaussian kernel with FWHM of \unit[3.0]{mm}.
    }
    \label{fig:grp_ao_av_c1_volsurf}
\end{figure*}

>>>>

\todo[inline]{only Captions mention smoothing of union of PPAs; Volume FWHM was
2mm, Surface FWHM was 3mm; I changed that to 2mm; plotting scripts need to be
rerun}

@@

% figure group results, volume, primary AD & AV contrasts
\begin{comment}

\begin{figure*}[tbp] \centering
    \includegraphics[width=\linewidth]{figures/group-slices}

@@

\end{comment}

% figure group results, volume & surface, primary AD & AV contrasts
\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/group-slices-volsurf}

    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
      cluster-corrected) of activity correlated with the processing of spatial
      information.
      a) Results are displayed on top of the MNI152 T1-weighted head template,
      with the acquisition field-of-view for the audio-description study
      highlighted.
      The results of the audio-description's primary $t$-contrast (blue) that
      compares geometry-related nouns spoken by the narrator to non-spatial
      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
      on the movie's primary $t$-contrast (red) that compares cuts to a
      setting depicted for the first time with cuts within a recurring setting
      (\texttt{vse\_new > vpe\_old}).
      % PPA
      For comparison depicted as a black outline, the union of the
      individual PPA localization reported by \citet{sengupta2016extension}
      that was spatially smoothed applying a Gaussian kernel with full
      width at half maximum (FWHM) of \unit[2.0]{mm}
      % surface map
      b) The results are displayed as projections onto the reconstructed
      surface of the MNI152 T1-weighted brain template. After projection the
      union of individual PPA localizations was spatially smoothed by a
      Gaussian kernel with FWHM of \unit[2.0]{mm}.
    }
    \label{fig:grp_ao_av_c1_volsurf}
\end{figure*}
